Adolescent well-being in the digital age

### 2022-03-21 associations.Rmd
bump

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(ggstance)
library(mgcv)
library(brms)
library(cmdstanr)
library(ellipse)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(emmeans)
library(broom)
library(tidyverse)
```

```{r load}
#| cache: false
# Load data sets
itu <- read_rds("data/itu.rds")
gwp <- read_rds("data/gwp.rds")
gbd <- read_rds("data/gbd.rds")

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  mutate(
    fit1 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-1-internet.rds"))
    ),
    fit2 = map(
      outcome, 
      ~read_rds(str_glue("models/brm-{.x}-2-internet.rds"))
    )
  )
```

@@

## Model comparison

First, we compared the R2 values between Models 1 and 2. This comparison is not perfect because the datasets differed slightly (each country had at least 1 fewer values in Model 2 because of the inclusion of the lagged internet predictor in Model 2). However it gives a rough idea of the added explanatory power of internet adoption on the well-being outcomes.

```{r model21-compare}
#| results: hold
#| tbl-cap: "Model 1 and 2 proportions variance explained by outcome"
#| label: tbl-m12-r2

fits %>%
  select(outcome, fit1, fit2) %>% 
  pivot_longer(c(fit1, fit2)) %>% 
  mutate(
    r2 = map(
      value,
      ~ bayes_R2(., resp = "val") %>%
        as.data.frame() %>%
        mutate(across(everything(), ~ percent(., .1))) %>%
        transmute(result = str_glue("{Estimate} [{Q2.5}, {Q97.5}]"))
    )
  ) %>%
  select(-value) %>%
  unnest(r2) %>% 
  pivot_wider(
    names_from = name,
    values_from = result,
    names_prefix = "Model "
  ) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  kbl(caption = "Model 1 and 2 R-squared values") %>%
  kable_custom()
fits <- select(fits, -fit1)
```

## Forest plot

We then display summaries of the parameters' posterior distributions as forest plots, like above. Recall the scales of the variables: Internet adoption is a proportion (0-1), and outcomes are percentages (0-100).

```{r forest-internet}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Forest plot of internet associations"
#| label: fig-forest-internet

# Calculate parameters at all levels of analysis
p_draws <- fits %>%
  mutate(pdraws = map(fit2, ~pdraws(.x, "i1_cw"))) %>%
  select(outcome, pdraws) %>%
  unnest(pdraws)
p_sums <- fits %>%
  mutate(psums = map(fit2, ~psums(.x, "i1_cw"))) %>%
  select(outcome, psums) %>%
  unnest(psums)
p_draws <- p_draws %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))
p_sums <- p_sums %>%
  mutate(region = fct_relevel(region, "Average")) %>%
  mutate(outcome = str_replace(outcome, "_", " ")) %>%
  mutate(outcome = factor(outcome, levels = str_replace(oo, "_", " ")))

p_draws %>%
  mutate(is_average = region == "Average") %>%
  ggplot(aes(value, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) {
      if_else(x == "Average", "**Average**", x) %>%
        str_replace("_", " ")
    }
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels",
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  # Add country points
  geom_point(
    data = p_sums %>%
      drop_na(country) %>%
      mutate(is_average = TRUE),
    aes(x = Estimate), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_richtext(
    data = p_sums %>%
      filter(is.na(country)) %>%
      mutate(is_average = region == "Average") %>%
      mutate(
        across(
          where(is.numeric),
          ~ if_else(
            outcome == "Selfharm",
            percent(. / 100, .001),
            percent(. / 100, .01)
          )
        )
      ),
    family = Font,
    alpha = 1, size = 3, hjust = 1, vjust = 0.2,
    fill = NA, label.color = NA,
    aes(
      x = Inf,
      label = str_glue("{Estimate}<br>[{Q2.5}, {Q97.5}]")
    )
  ) +
  facet_wrap(
    "outcome",
    nrow = 2, scales = "free_x"
  ) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
x <- percent(fixef(fits$fit2[[1]])["i1_cw",-2]/100)
x2 <- percent(hypothesis(fits$fit2[[3]], "i1_cw > 0")$hypothesis$Post.Prob, .1)
```

This figure shows that, on the whole, the predictive associations between internet adoption and well-being were somewhat small. First, on average across regions and countries, a 100% increase in internet adoption was associated with a `r x[1]` increase in life satisfaction, but with 95% confidence this number could range from `r x[2]` to `r x[3]`. However, in the African region, increased internet adoption was associated with increases in life satisfaction at a confidence level exceeding 95%. Somewhat confusingly, internet adoption was positively associated with negative experiences also in the African region. However, none of the average associations were credibly different from zero. The association between internet adoption and positive experiences came closest with a `r x2` posterior probability of a positive association.

## Counterfactual plot

To help illustrate the magnitudes of associations, we draw figures of the fitted lines, or so called counterfactual plots.

```{r model2-fitted-values}
#| column: screen-inset-right
#| fig-width: 13
#| fig-height: 8
#| fig-cap: "Counterfactual plot of internet associations"
#| label: fig-fitted-internet

fitted_country <- function(x) {
  newx <- x$data %>%
    group_by(country) %>%
    mutate(
      xmin = min(i1_cw, na.rm = TRUE),
      xmax = max(i1_cw, na.rm = TRUE)
    ) %>%
    filter(i1_cw %in% c(xmin, xmax)) %>%
    ungroup() %>%
    distinct(country, region, outcome, i1_cw, i1_cb) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)
  newy <- bind_cols(newx, as.data.frame(fitted(x, newdata = newx))) %>%
    select(-outcome)
  newy
}

fitted_region <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region) %>%
    summarise(i1_cb = mean(i1_cb, na.rm = TRUE)) %>%
    crossing(i1_cw = seq(-.4, .4, length = 10)) %>%
    mutate(year = 0, sex = NA, age = NA, se = 0)

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = ~ 
          (year * sex + year * age + i1_cw * sex + i1_cw * age | region)
        )
    )
  ) %>%
    select(-outcome)
  newy
}

f_country <- fits %>%
  mutate(fc = map(fit2, fitted_country)) %>%
  select(outcome, fc) %>%
  unnest(fc)

f_region <- fits %>%
  mutate(fr = map(fit2, fitted_region)) %>%
  select(outcome, fr) %>%
  unnest(fr)

f_country %>%
  ggplot(aes(i1_cw, Estimate)) +
  scale_x_continuous(
    "Previous year's internet adoption relative to country average in 2000-2020",
    breaks = c(-.35, 0, .35),
    labels = function(x) percent(x, 1)
  ) +
  scale_y_continuous(
    "Estimate",
    breaks = pretty_breaks(),
    labels = function(x) percent(x / 100, .01) %>% str_remove("\\.00")
  ) +
  geom_blank() +
  geom_ribbon(
    data = f_region,
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .15, fill = "dodgerblue4"
  ) +
  geom_line(
    data = f_region,
    col = "dodgerblue4", size = .6
  ) +
  geom_line(
    aes(group = country),
    size = .4, alpha = .35, col = "dodgerblue1"
  ) +
  facet_grid(
    outcome ~ region,
    scales = "free_y",
    labeller = as_labeller(function(x) str_replace(x, "_", "\n"))
  ) +
  theme(
    panel.spacing = unit(2, "pt"),
    axis.title.y = element_blank()
  )
```

@@

fitted_cb1 <- function(x) {
  newx <- x$data %>%
    group_by(outcome, region, country) %>%
    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        x, 
        newdata = newx, 
        re_formula = NA
        )
    )
  ) %>%
    select(-outcome)
  newy
}
tmp <- fits %>% 
  mutate(out = map(fit2, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

cb1_pars <- fits %>%
  mutate(
    out = map(
      fit2,
      ~ as_draws_df(
        .x,
        variable = "b_i1_cb"
      ) %>%
        summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
    )
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(i1_cb, val)) +
  scale_x_continuous(
    "Between-country centered internet adoption",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100)
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
    ) +
  geom_line(aes(y = Estimate), col = "dodgerblue4") +
  geom_text(
    data = cb1_pars,
    aes(x = -Inf, y = Inf, label = str_glue("{mean} [{q2.5}, {q97.5}]")),
    vjust = 1.3, hjust = -0.025, family = Font
  ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 2,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )
```

>>>>

```{r setup}
#| cache: false
# Packages
library(scales)
library(ggtext)
library(lubridate)
library(kableExtra)
library(memoise)
library(cachem)
library(ggstance)
library(ggbeeswarm)
library(mgcv)
library(brms)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(bayestestR)
library(emmeans)
library(broom)
library(tidyverse)

cd <- cache_disk("memoise_cache", max_size = Inf)
```

```{r load}
#| cache: false
# Load data sets
dat <- read_rds("data/data-all.rds")

# Countries and regions
countries <- dat %>% 
  distinct(region, country)

# Load models
oo <- c(
  "Life_satisfaction", "Negative_experiences", "Positive_experiences",
  "Anxiety", "Depression", "Selfharm"
)
fits <- tibble(outcome = oo) %>% 
  mutate(outcome = factor(outcome, levels = oo))
```

@@

## Main result: Association

```{r}
get_fixef <- function(outcome, var = "i1_cw"){
  path <- str_glue("models/brm-{outcome}-2-internet.rds")
  fixef(
    readRDS(path), 
    summary = FALSE
  )[,var, drop = FALSE] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_fixef <- memoise(get_fixef, cache = cd)

fits_fixef <- fits %>% 
  mutate(out = map(outcome, ~get_fixef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)

fits_fixef %>%
  mutate(across(mean:q97.5, ~./10)) %>% 
  kbl(digits = 2, caption = "Model 2 population level associations (% increase per 10% increase in internet adoption)") %>% 
  kable_custom()
```

This table shows the population-level (average across region, country, age) associations. We then summarise the region- and country-level trends in a table.

```{r}
# Region coefficients
get_region_coef <- function(outcome) {
  path <- str_glue("models/brm-{outcome}-2-internet.rds")
  coef(readRDS(path), summary = FALSE)$region[,,"i1_cw"] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_region_coef <- memoise(get_region_coef, cache = cd)

i1_cw_region <- fits %>% 
  mutate(out = map(outcome, ~get_region_coef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)
i1_cw_region <- rename(i1_cw_region, region = variable)

# Country random deviations + region coefficients
get_country_ranef <- function(outcome) {
  path <- str_glue("models/brm-{outcome}-2-internet.rds")
  ranef(readRDS(path), summary = FALSE)$country[,,"i1_cw"] %>% 
    summarise_draws(
      mean, sd,
      ~quantile2(., probs = c(.025, .1, .5, .9, .975)),
      pd = ~pd(as.numeric(.)), 
      rhat
    ) %>% 
    mutate(pd = percent(pd, .1))
}
get_country_ranef <- memoise(get_country_ranef, cache = cd)

i1_cw_country <- fits %>% 
  mutate(out = map(outcome, ~get_country_ranef(.x))) %>% 
  select(outcome, out) %>% 
  unnest(out)

# Add region coefs
i1_cw_country <- i1_cw_country %>% 
  rename(country = variable) %>% 
  left_join(countries) %>% 
  left_join(
    select(i1_cw_region, outcome, region, mean_region = mean)
  ) %>% 
  mutate(across(mean:q97.5, ~. + mean_region)) %>% 
  # pd doesn't work without the region coefs
  select(-mean_region, -pd)

i1_cw_region %>% 
  mutate(across(mean:q97.5, ~./10)) %>% 
  arrange(outcome, mean) %>% 
  kbl(
    digits = 2, 
    caption = "Region-specific associations, arranged by outcome and magnitude"
  ) %>% 
  kable_custom() %>% 
  scroll_box("500px")

i1_cw_country %>% 
  mutate(across(mean:q97.5, ~./10)) %>% 
  select(outcome, country, everything()) %>% 
  arrange(outcome, mean) %>% 
  kbl(
    digits = 2, 
    caption = "Country-specific associations, ordered by outcome and magnitude"
  ) %>% 
  kable_custom() %>% 
  scroll_box("500px")
```

### Coefficient plot

Putting these together into a plot

```{r}
tmp <- i1_cw_country %>%
  mutate(Level = "Country") %>% 
  mutate(s = sign(q2.5) == sign(q97.5))

bind_rows(
  "Average" = fits_fixef %>% mutate(region = "**Average**"),
  "Region" = i1_cw_region,
  .id = "Level"
) %>% 
  mutate(region = fct_relevel(region, "**Average**")) %>% 
  mutate(s = sign(q2.5) == sign(q97.5)) %>% 
  ggplot(aes(mean, region, col = Level, shape = s)) +
  scale_color_manual(
    values = c("dodgerblue4", "dodgerblue3", "dodgerblue3")
  ) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    labels = ~str_replace(., "_", " "),
    expand = expansion(c(0.05, 0.05))
  ) +
  scale_x_continuous(
    "Conditional lagged effect of 10% increase in internet adoption",
    breaks = pretty_breaks(5),
    # Effect of 10% increase
    labels = function(x) percent(x / 1000, .001) %>% 
      str_remove("\\.000") %>% 
      str_remove("(?<=[0-9])0(?=%)"),
    expand = expansion(c(0.025, .025))
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  geom_point(
    data = tmp,
    size = 1, col = "dodgerblue1", stroke = .3, alpha = .8,
    position = position_quasirandom(width = .2, groupOnX = F)
  ) +
  geom_linerange(
    aes(xmin = q10, xmax = q90), size = 1, col = "dodgerblue4"
  ) +
  geom_pointrangeh(
    aes(xmin = q2.5, xmax = q97.5), col = "dodgerblue4",
    fatten = 4, fill = "white", stroke = .8
  ) +
  # geom_richtext(
  #   aes(x = Inf, label = str_glue("{percent(mean/100, .01)}<br>[{percent(q2.5/100, .01)} {percent(q97.5/100, .01)}]")), 
  #   hjust = 1, vjust = 0.15, size = 2.7, lineheight = .9,
  #   col = "black", fill = NA, label.color = NA
  # ) +
  facet_wrap(
    "outcome", scales = "free_x", ncol = 3,
    labeller = as_labeller(~str_replace(., "_", " "))) +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
agg_png(
  "Fig-assc-coef.png", 
  width = W, height = W*0.6, units = "in", res = 400
)
last_plot()
dev.off()
```

@@

fitted_cb1 <- function(outcome) {
  fit <- readRDS(str_glue("models/brm-{outcome}-2-internet.rds"))
  newx <- fit$data %>%
    group_by(region, country) %>%
    summarise(i1_cb = unique(i1_cb), val = mean(val, na.rm = TRUE)) %>% 
    mutate(i1_cw = 0, year = 0, sex = NA, age = NA, se = 0) %>% 
    ungroup()

  newy <- bind_cols(
    newx,
    as.data.frame(
      fitted(
        fit, 
        newdata = newx, 
        re_formula = NA
      )
    )
  )
  newy
}
fitted_cb1 <- memoise(fitted_cb1, cache = cd)

tmp <- fits %>% 
  mutate(out = map(outcome, fitted_cb1)) %>% 
  select(outcome, out) %>%
  unnest(out)

get_cor_par <- function(outcome) {
  as_draws_df(
    readRDS(str_glue("models/brm-{outcome}-2-internet.rds")),
    variable = "b_i1_cb"
  ) %>%
    summarise_draws(mean, sd, ~ quantile2(., probs = c(.025, .975)))
}
get_cor_par <- memoise(get_cor_par, cache = cd)

cb1_pars <- fits %>%
  mutate(
    out = map(outcome, ~get_cor_par(.x))
  ) %>%
  select(outcome, out) %>%
  unnest(out) %>%
  mutate(across(where(is.numeric), ~ number(., .01)))

tmp %>% 
  ggplot(aes(i1_cb, val)) +
  scale_x_continuous(
    "Between-country centered internet adoption",
    labels = ~percent(.)
  ) +
  scale_y_continuous(
    "Value",
    labels = ~percent(./100),
    breaks = extended_breaks()
  ) +
  geom_point(
    shape = 1, size = 1, alpha = .75, col = "dodgerblue1"
  ) +
  geom_ribbon(
    aes(ymin = Q2.5, ymax = Q97.5),
    alpha = .2, fill = "dodgerblue1"
  ) +
  geom_line(
    aes(y = Estimate), 
    col = "dodgerblue4", size = 1
  ) +
  geom_smooth(
    method = "lm", se = F, 
    size = .5, col = "black", lty = 2
  ) +
  # geom_text(
  #   data = cb1_pars,
  #   aes(
  #     x = -Inf, 
  #     y = Inf, 
  #     label = str_glue("{mean} [{q2.5}, {q97.5}]")
  #   ),
  #   vjust = 1.3, hjust = -0.025, size = 2.8, family = Font
  # ) +
  facet_wrap(
    "outcome",
    scales = "free_y", nrow = 1,
    labeller = as_labeller(~str_replace(., "_", " "))
  ) +
  theme(
    aspect.ratio = 1,
    axis.title.y = element_blank()
  )

agg_png(
  "Fig-assc-cor.png", 
  width = W, height = W*0.2, units = "in", res = 400
)
last_plot()
dev.off()
```

Here are these correlations calculated from data

```{r}
# From data
tmp <- dat %>% 
  mutate(outcome = factor(outcome, levels = oo)) %>% 
  group_by(outcome, country) %>% 
  summarise(
    val = mean(val, na.rm = TRUE),
    internet = mean(i1_cb, na.rm = TRUE)
  )
tmp_tab <- tmp %>% 
  summarise(
    tidy(lm(scale(val) ~ scale(internet), data = cur_data()), conf.int = TRUE)
  ) %>% 
  ungroup() %>%
  filter(term != "(Intercept)") %>% 
  mutate(across(where(is.numeric), ~number(., .01))) %>% 
  transmute(
    Outcome = str_replace(outcome, "_", " "),
    r_CI = str_glue("{estimate}, [{conf.low}, {conf.high}]")
  )
tmp_tab
tmp_tab %>% 
  flextable::flextable(cwidth = 2) %>% 
  flextable::save_as_docx(path = "tmp.docx")
```
